Strong lensing selection effects

### 2022-07-09 paper/seleff.tex
reorganized secgtion 2

The structure of this work is the following.
In \Sref{sect:indlenses} we study individual lens systems, to look for trends in the lensing cross-section with various lens and source properties.
In \Sref{sect:lenspop} we describe our simulations of lens populations.
In \Sref{sect:results} we show the results of our analysis on the simulated lens populations.
We discuss the results in \Sref{sect:discuss} and draw conclusions in \Sref{sect:concl}.

@@

@@

In this section we compute $\crosssect$ in a series of different scenarios of increasing complexity.
We first introduce the basic equations of gravitational lensing in section \ref{ssec:lensbasics}.
Then, in section \ref{ssec:profile}, we present the model family adopted to describe the radial density profile of the lenses in our experiments.
%The model family adopted to describe the radial density profile of the lenses is the same in all of our experiments. We describe this in \ref{ssec:profile}, among with the basic equations of gravitational lensing.
%In section \ref{ssec:axsymmpoint} we consider axisymmetric lenses and point sources.
In section \ref{ssec:axsymmpoint} we show calculations of the strong lensing cross-section in the case of axisymmetric lenses and point sources.
In section \ref{ssec:ellpoint} we generalise the lens geometry to elliptical, while in section \ref{ssec:ellext} we replace point sources with extended sources.

\subsection{Strong lensing basics}\label{ssec:lensbasics}

>>>>

The structure of this work is the following.
\Sref{sect:basics} introduces the basics of gravitational lensing.
In \Sref{sect:indlenses} we study individual lens systems, to look for trends in the lensing cross-section with various lens and source properties.
In \Sref{sect:lenspop} we describe our simulations of lens populations.
In \Sref{sect:results} we show the results of our analysis on the simulated lens populations.
We discuss the results in \Sref{sect:discuss} and draw conclusions in \Sref{sect:concl}.

@@

\section{Strong lensing basics}\label{sect:basics}

\subsection{The axisymmetric lens}

\subsection{The elliptical lens}

@@

In this section we compute $\crosssect$ in a series of different scenarios of increasing complexity.
%We first introduce the basic equations of gravitational lensing in section \ref{ssec:lensbasics}.
%Then, in section \ref{ssec:profile}, we present the model family adopted to describe the radial density profile of the lenses in our experiments.
The model family adopted to describe the radial density profile of the lenses is the same in all of our experiments. We describe this in \ref{ssec:profile}. %, among with the basic equations of gravitational lensing.
%In section \ref{ssec:axsymmpoint} we consider axisymmetric lenses and point sources.
In section \ref{ssec:axsymmpoint} we show calculations of the strong lensing cross-section in the case of axisymmetric lenses and point sources.
In section \ref{ssec:ellpoint} we generalise the lens geometry to elliptical, while in section \ref{ssec:ellext} we replace point sources with extended sources.

%\subsection{Strong lensing basics}\label{ssec:lensbasics}
